Verification of the CVM algorithm with a Functional Probabilistic Invariant

### 2025-06-20 paper/main.tex
Fill in author information

% TODO: put in everyone's names here

\author{Yong Kiam Tan}{Institute for Infocomm Research (I$^2$R), A*STAR, Singapore \and Nanyang Technological University, Singapore}{yongkiam.tan@ntu.edu.sg}{https://orcid.org/0000-0001-7033-2463}{Singapore NRF Fellowship Programme NRF-NRFF16-2024-0002}
% \author{Seng Joe Watt}{Institute for Infocomm Research (I$^2$R), A*STAR, Singapore \and Nanyang Technological University, Singapore}{yongkiam.tan@ntu.edu.sg}{https://orcid.org/0000-0001-7033-2463}{Singapore NRF Fellowship Programme NRF-NRFF16-2024-0002}

\author{\textcolor{red}{Anonymous author(s)}}{\textcolor{red}{Anonymous affiliation(s)}}{}{}{}

\authorrunning{\textcolor{red}{Anonymous author(s)}} %TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'

\Copyright{\textcolor{red}{Anonymous author(s)}} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

>>>>

% TODO: put in everyone's names here
\author{Emin Karayel}{Technical University of Munich, Department of Computer Science, Germany}{me@eminkarayel.de}{https://orcid.org/0000-0003-3290-5034}{}
\author{Seng Joe Watt}{Institute for Infocomm Research (I$^2$R), A*STAR, Singapore}{Watt_Seng_Joe@i2r.a-star.edu.sg}{https://orcid.org/0000-0002-6883-4736}{TODO}
\author{Yong Kiam Tan}{Institute for Infocomm Research (I$^2$R), A*STAR, Singapore \and Nanyang Technological University, Singapore}{yongkiam.tan@ntu.edu.sg}{https://orcid.org/0000-0001-7033-2463}{Singapore NRF Fellowship Programme NRF-NRFF16-2024-0002}
\author{Kuldeep S. Meel}{Georgia Institute of Technology \and University of Toronto}{meel@cs.toronto.edu}{https://orcid.org/0000-0001-9423-5270}{TODO}
\author{Derek Khu}{Institute for Infocomm Research (I$^2$R), A*STAR, Singapore}{derek_khu@i2r.a-star.edu.sg}{https://orcid.org/0009-0000-0293-0664}{TODO}

\authorrunning{E. Karayel, S. J. Watt, Y. K. Tan, K. S. Meel, D. Khu} %TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'

\Copyright{Emin Karayel, Seng Joe Watt, Yong Kiam Tan, Kuldeep S. Meel, Derek Khu} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
